\documentclass{ExpressiveResume}

% Use Arial (Helvetica) font
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

% Make section headers bold with dark blue color and underline
\usepackage{titlesec}
\usepackage{xcolor}
\definecolor{darkblue}{RGB}{0, 51, 102}
\titleformat{\section}{\Large\bfseries\color{darkblue}}{}{0em}{}[\color{darkblue}\titlerule]

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=Khanh Nguyen (Alex),
    middleinitial=,
    lastname=Bui,
    email=kbui0173@gmail.com,
    phone=+61-436-468-715,
    linkedin=khanh-alex-nguyen-bui-4858b6390,
    github=kbui0173,
    website=https://kbui0173.github.io/,
    city=Chippendale,
    state=NSW,
]

\objective{A dedicated Business Analytics and Data Science student with strong analytical thinking and problem-solving skills. Seeking opportunities to apply statistical modeling, predictive analytics, and data-driven insights to business challenges.}

% ----- Education -----
\section{Education}

\degree{Bachelor of Commerce}{Grade:\textbf{ Distinction}}{The University of Sydney}{Feb 2024 - July 2026}{}{
    \achievement{\textbf{Major:} Business Analytics and Data Science}
    \achievement{\textbf{Relevant Topics:} Statistical Modeling, Integer/Non-Integer Optimization, Dynamic Programming, Stochastic Processes, Bayesian Inference, Generalized Linear Models, Time Series Analysis, Option Pricing, Machine Learning.}
}

% ----- Technical Skills -----
\section{Skills \& Interest}

\skill{Technical Skills}{\tech{Python}, \tech{R}, \tech{SQL}, \LaTeX, Quarto, Git.}
\skill{Academic Interest}{Time Series Analysis, Portfolio Optimization, Machine Learning, Option Pricing.}
\skill{Other Interests}{Golf, Photography, Poker.}

% ----- Projects -----
\section{Technical Projects}

\project{Australian CPI Forecasting}{Nov, 2025}{
    \achievement{
        Developed an ARIMA forecasting pipeline for Australian CPI data using Python, Statsmodels, and Pandas.
    }
    \achievement{
        Implemented exhaustive grid search with expanding window cross-validation to identify optimal hyperparameters.
    }
    \achievement{
        Surpassed baseline model performance by reducing Mean Squared Error (MSE) through out-of-sample validation.
    }
    \achievement{
        \textbf{Tools Used:} \tech{Python} (Statsmodels, Pandas, Scikit-learn, Matplotlib, Seaborn), Quarto, GitHub Pages
    }
    \achievement{
        \textbf{Technical Skills:} Time Series Modeling, Expanding Window Cross-Validation, Data Visualization.
    }
}{https://kbui0173.github.io/projects/project-1/}

\project{Regime-Switching Volatility Forecasting}{Dec, 2025}{
    \achievement{
        Fetched market data using Quantmod and wrote scripts to resolve timezone-related date errors.
    }
    \achievement{
        Applied Hidden Markov Models within a GJR-GARCH framework to forecast volatility and identify distinct market stress regimes.
    }
    \achievement{
        Selected Skewed Student-t distributions to accurately model 'fat tails' and asymmetry in market data.
    }
    \achievement{
        Reduced MSE by 1.35\% against single-regime benchmarks via parallelized expanding window cross-validation.
    }
    \achievement{
        \textbf{Tools Used:} \tech{R} (MSGARCH, Quantmod, Tidyverse, doParallel, Plotly), Quarto
    }
    \achievement{
        \textbf{Technical Skills:} Volatility Modeling, Hidden Markov Models, Parallel Computing.
    }
}{https://kbui0173.github.io/projects/project-2/}


% ----- Experience -----
\section{Experience}

\experience{Receptionist}{BeBee Co-Working Space - HCMC, Vietnam}{May 2025 - Sep 2025}{
    \achievement{
        Met and greeted up to 200+ guests daily to ensure they received a warm and friendly welcome.
    }
    \achievement{
        Took time to understand the needs of each visitor and offered additional information.
    }
    \achievement{
        Kept accurate records on check-ins and maintained data confidentiality.
    }
    \achievement{
        Worked as part of a team of 5 and motivated others whenever possible.
    }
}

\experience{Waiter}{Ngon 138 Restaurant - HCMC, Vietnam}{May 2024 - Sep 2024}{
    \achievement{
        Served customers and addressed complaints to improve customer service.
    }
    \achievement{
        Developed verbal communication skills by engaging with manager and kitchen staff to stay up-to-date on supply availability.
    }
    \achievement{
        Developed time management skills to minimize customer wait times.
    }
}

\experience{Full-time Junior Golfer}{MMG Performance - Orlando, Florida}{Jun 2019 - Dec 2021}{
    \achievement{
        Trained with world-class coaches and competed in various junior tournaments.
    }
    \achievement{
        Achieved the best personal ranking of 7th in Disney Summer Junior Open (+10 over two rounds).
    }
    \achievement{
        Developed self-discipline through training and mental toughness through competition.
    }
}   

\end{document}